cardinalR: Generating interesting high-dimensional data structures

### 2025-10-22 paper-cardinalR.Rmd
Updated Figure 7 title

```{r sphere-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `circle` (a1-a3), `curvycycle` (b1-b3), `unifsphere` (c1-c3), `gridedsphere` (d1-d3), `clusteredspheres` (e1-e3), and `hemisphere` (f1-f3) data.", fig.width=12, fig.height=12, out.width="100%", fig.align='center', fig.pos="H"}

@@

curvycylinder_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.5), 
  title = "b1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

curvycylinder_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "b2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

curvycylinder_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.5), 
  title = "b3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

sphericalspiral_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "c1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

sphericalspiral_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "c2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

sphericalspiral_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.5), 
  title = "c3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

conicspiral_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "e1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

conicspiral_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.8, 0.5), 
  title = "e2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

conicspiral_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.6, 0.62), 
  title = "e3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

nonlinear_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.45, 0.73), 
  title = "f1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

nonlinear_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.3, 0.46), 
  title = "f2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

nonlinear_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.35, 0.4), 
  title = "f3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

```{r triginometric-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `crescent` (a1-a3), `curvycylinder` (b1-b3), `sphericalspiral` (c1-c3), `helicalspiral` (d1-d3), `conicspiral` (e1-e3), and `nonlinear` (f1-f3) data.", fig.width=12, fig.height=16, out.width="100%", fig.align='center', fig.pos="H"}

>>>>

```{r sphere-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `circle` (a1-a3), `curvycycle` (b1-b3), and, `clusteredspheres` (c1-c3).", fig.width=12, fig.height=12, out.width="100%", fig.align='center', fig.pos="H"}

@@

curvycylinder_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.5), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

curvycylinder_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

curvycylinder_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.5), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

sphericalspiral_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "b1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

sphericalspiral_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "b2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

sphericalspiral_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.5), 
  title = "b3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

conicspiral_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "c1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

conicspiral_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.8, 0.5), 
  title = "c2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

conicspiral_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.6, 0.62), 
  title = "c3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

nonlinear_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.45, 0.73), 
  title = "d1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

nonlinear_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.3, 0.46), 
  title = "d2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

nonlinear_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.35, 0.4), 
  title = "d3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

```{r triginometric-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `curvycylinder` (a1-a3), `sphericalspiral` (b1-b3), `conicspiral` (c1-c3), and `nonlinear` (d1-d3) data.", fig.width=12, fig.height=16, out.width="100%", fig.align='center', fig.pos="H"}

### 2025-10-22 paper-cardinalR.tex
Updated Figure 7 title

\caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `circle` (a1-a3), `curvycycle` (b1-b3), `unifsphere` (c1-c3), `gridedsphere` (d1-d3), `clusteredspheres` (e1-e3), and `hemisphere` (f1-f3) data.}\label{fig:sphere-proj}
\end{figure}

@@

\caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `crescent` (a1-a3), `curvycylinder` (b1-b3), `sphericalspiral` (c1-c3), `helicalspiral` (d1-d3), `conicspiral` (e1-e3), and `nonlinear` (f1-f3) data.}\label{fig:triginometric-proj}
\end{figure}

>>>>

\caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `circle` (a1-a3), `curvycycle` (b1-b3), and, `clusteredspheres` (c1-c3).}\label{fig:sphere-proj}
\end{figure}

@@

\caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `curvycylinder` (a1-a3), `sphericalspiral` (b1-b3), `conicspiral` (c1-c3), and `nonlinear` (d1-d3) data.}\label{fig:triginometric-proj}
\end{figure}
